### 2022-10-19 manuscript.Rmd
mock make workflow for cluster

classoption       : "man"
output            : papaja::apa6_pdf
repro:
  packages:
    - papaja
    - tidyverse
    - ggpubr
    - SimDesign
    - here
  tlmgr:
    - apa6
    - threeparttable
    - endfloat
    - framed
    - was
    - multirow
    - threeparttablex
    - environ
    - trimspaces
    - xpatch
    - csquotes
  scripts:
    - R/funs.R
    - "01_run_simulation.R"
---

@@

In a second step, we further examined the effect of the construct reliability on statistical power by investigating the loading strength of the manifest variables. To this end we conducted a second simulation following the steps outlined above while varying the sample size from 50 to 200 and the loadings of the manifest variables from 0.5 to 0.9. Figure 3B displays the obtained power curves, illustrating statistical power dependent on total sample size and loading strength of the manifest variables. For this estimate, the factor inter-correlation was set to 0.3. Again, increasing sample size lead to higher statistical power. However, the loading strength impacted estimates of statistical power: the higher the loadings of the manifest variables, the higher the statistical power achieved by a given sample size. For reasonably high levels of factor loadings (>= 0.7) a statistical power of 95% was reached for *N* = 120.

>>>>

classoption       : "man"
output            : papaja::apa6_pdf
repro:
  packages:
    - papaja
    - tidyverse
    - ggpubr
    - SimDesign
    - here
  tlmgr:
    - apa6
    - threeparttable
    - endfloat
    - framed
    - was
    - multirow
    - threeparttablex
    - environ
    - trimspaces
    - xpatch
    - csquotes
  scripts:
    - R/funs.R
    - R/run_simulation.R
  files:
    - intermediate_results.zip
---

@@

In a second step, we further examined the effect of the construct reliability on statistical power by investigating the loading strength of the manifest variables. To this end we conducted a second simulation following the steps outlined above while varying the sample size from 50 to 200 and the loadings of the manifest variables from 0.5 to 0.9. Figure 3B displays the obtained power curves, illustrating statistical power dependent on total sample size and loading strength of the manifest variables. For this estimate, the factor inter-correlation was set to 0.3. Again, increasing sample size lead to higher statistical power. However, the loading strength impacted estimates of statistical power: the higher the loadings of the manifest variables, the higher the statistical power achieved by a given sample size. For reasonably high levels of factor loadings (>= 0.7) a statistical power of 95% was reached for *N* = 120. 
```{r}
intermediate_results <- here("intermediate_results/")
if(fs::dir_exists(intermediate_results))
  fs::dir_delete(intermediate_results)
unzip(here("intermediate_results.zip"))
```
